Title here

### 2017-05-19 portfolio/text/ms.Rmd
Fixed typos

Using a unique dataset collected over 30 years on individual fishers, rather 
than fleets or vessels, we examine how revenue and revenue variability of 
individuals is affected by diversification. By tracking individuals, it is
possible to track people that switch fishery permits over time or use multiple
vessels and differentiate fishers that share the same vessel. We developped and
applied a hierarchical Bayesian model to understand the effect of species
diversity within fisheries catches on individual revenue and revenue
variability. Our model builds on results from vessel [@kasperski2013], fleet
[@sethi2012b], and community-level [@sethi2014; @cline2017] variability. We
developped a variance-function regression model [@davidian1987; @hall1989], to
simultaneously model changes in the mean and variance of individual revenue as a
function of covariates. We simultaneously estimate the effect of species
diversity (the inverse of Simpson's diversity index [@simpson1949; @jost2006])
on individual revenue and revenue variability, and estimate effects both within
and across fishing strategies while controlling for fishing effort and latent
time effects (e.g. changing environmental conditions). We use the model to evaluate two axes by which fishers in Alaska can diversify fishing activities:
(1) choice of permit strategy (i.e., permit or set of permits fished), and (2)
choice of what species to fish *within* a permit strategy. To our knowledge,
this is the first application of this type of model in any natural resource
field.

@@

Our findings across fishing strategies are in line with previous research at the
community and vessel levels [@kasperski2013; @sethi2012b; @sethi2014; @cline2017], but our
findings within strategies, with respect to individual year-to-year behavior,
provide new insights. Here, specializing tended to be associated with increased
revenue. This could be for a number of reasons. First, specialization can
increase fishing efficiency [@smith1986]. 
Similar efficiency gains from specialization are well known in 
agricultural fields [@ikerd1990; @abdulai2000].
Second, given the
availability of valuable resources, specializing can be highly profitable. For
instance, when cocoa prices have been high, Nigerian farmers have tended to
specialize on the crop [@mustapha1999] and specializing on valuable tobacco
farming can be the optimal strategy regardless of alternative crops
[@chavez2014]. In our analyses, fishers with the opportunity to fish highly
valuable sockeye salmon benefited the most from specializing. However,
specializing can have longterm risks if market, management, biological, or
environmental conditions change. For example, U.S. farmers specialized on wheat,
corn, or soybeans were hit harder than diversified farmers in the early 1980s
when a financial crisis hit [@ikerd1990].
Third, diversifying---a lack of
specialization---can happen as a consequence of non-ideal circumstances such
as poor availability of a more valuable resource. For example, Ugandan
households relying on forestry resources for income increase their income
portfolio diversity following downward economic shocks [@debela2012].
Because specialization inherently holds risk from ``putting all one's eggs in one
basket,'' it is not suprising that a decline in the most valuable resource
would lead to a shift towards diversification.
<!-- Response to A1 -->
Conversely, a specialization may appear as a response to increased revenue. A fisher who achieves high revenue from a hotspot of a particular fish species one year may choose to stop or pause fishing thereby indirectly limiting catch diversity. For example, pink and chum salmon are the dominant species caught in purse seine fisheries in Prince william Sound and their run timing rarely overlaps. If a fisher achieves high revenue with one species that fisher may cut the season short.

>>>>

Using a unique dataset collected over 30 years on individual fishers, rather 
than fleets or vessels, we examine how revenue and revenue variability of 
individuals is affected by diversification. By tracking individuals, it is
possible to track people that switch fishery permits over time or use multiple
vessels and differentiate fishers that share the same vessel. We developed and
applied a hierarchical Bayesian model to understand the effect of species
diversity within fisheries catches on individual revenue and revenue
variability. Our model builds on results from vessel [@kasperski2013], fleet
[@sethi2012b], and community-level [@sethi2014; @cline2017] variability. We
developped a variance-function regression model [@davidian1987; @hall1989], to
simultaneously model changes in the mean and variance of individual revenue as a
function of covariates. We simultaneously estimate the effect of species
diversity (the inverse of Simpson's diversity index [@simpson1949; @jost2006])
on individual revenue and revenue variability, and estimate effects both within
and across fishing strategies while controlling for fishing effort and latent
time effects (e.g. changing environmental conditions). We use the model to evaluate two axes by which fishers in Alaska can diversify fishing activities:
(1) choice of permit strategy (i.e., permit or set of permits fished), and (2)
choice of what species to fish *within* a permit strategy. To our knowledge,
this is the first application of this type of model in any natural resource
field.

@@

Our findings across fishing strategies are in line with previous research at the
community and vessel levels [@kasperski2013; @sethi2012b; @sethi2014; @cline2017], but our
findings within strategies, with respect to individual year-to-year behavior,
provide new insights. Here, specializing tended to be associated with increased
revenue. This could be for a number of reasons. First, specialization can
increase fishing efficiency [@smith1986]. 
Similar efficiency gains from specialization are well known in 
agricultural fields [@ikerd1990; @abdulai2000].
Second, given the
availability of valuable resources, specializing can be highly profitable. For
instance, when cocoa prices have been high, Nigerian farmers have tended to
specialize on the crop [@mustapha1999] and specializing on valuable tobacco
farming can be the optimal strategy regardless of alternative crops
[@chavez2014]. In our analyses, fishers with the opportunity to fish highly
valuable sockeye salmon benefited the most from specializing. However,
specializing can have longterm risks if market, management, biological, or
environmental conditions change. For example, U.S. farmers specialized on wheat,
corn, or soybeans were hit harder than diversified farmers in the early 1980s
when a financial crisis hit [@ikerd1990].
Third, diversifying---a lack of
specialization---can happen as a consequence of non-ideal circumstances such
as poor availability of a more valuable resource. For example, Ugandan
households relying on forestry resources for income increase their income
portfolio diversity following downward economic shocks [@debela2012].
Because specialization inherently holds risk from ``putting all one's eggs in one
basket,'' it is not suprising that a decline in the most valuable resource
would lead to a shift towards diversification.
<!-- Response to A1 -->
Conversely, a specialization may appear as a response to increased revenue.
A fisher who achieves high revenue from a hotspot of a particular fish species
one year may choose to stop or pause fishing thereby indirectly limiting catch
diversity. For example, pink and chum salmon are the dominant species caught in
purse seine fisheries in Prince William Sound, with chum salmon generally
harvested earlier in the season than pink salmon. If fishers targeting chum salmon
achieve high revenue early in the season, they may choose to fish less later in
the season.
